Contracts for Contracts

### 2023-04-27 paper.tex
suggesting another syntax for msg.sender

Solidity does provide first-order assertion primitives (e.g. @require@ or
@modifier@) but they cannot effectively check function values, which are a
common pattern used in smart contract programs. Programmers have to
manually insert such checks around relevant call-sites, \todo{which is bad}.
%Solidity also provides the @modifier@ mechanism that intercepts
%before and after a function call, thus can be used to check
%pre- and post-conditions.
%\todo{can we compose modifier?}
%\todo{can we attach modifier to callbacks?}
%\todo{can we use modifier to check function's argument?}

@@

\todo{restrict possible call targets}
\todo{why static verification fails}

@@

We develop a core model of the extension, including its syntax,
operational semantics, and discuss its soundness guarantee.
With this extension of higher-order temporal behavioral contracts, we examine
several cases of reported bugs and vulnerabilities and show that
our approach is effective in preventing these attacks.
We also evaluate the overhead (gas consumption) of our approach
compared to manually inserted assertion checks, showing that \todo{...}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
	\item We propose a specification of behavioral contracts for expressing and
	      enforcing higher-order and temporal properties for smart contracts.
	\item We design \lang, an extension for Solidity with
	      behavioral contracts, demonstrate its use cases through extensive examples,
	      and how it can improve the safety and reliability.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
	\item We examine a number of real-world attacks and show that our proposal is
	      effective in improving safety and reliability.
	\item We implement our approach on top of the existing Solidity compiler and shows
	      that its runtime overhead is marginal, therefore practical to use.
\end{itemize}

@@

When specifying the spec of functions, two special variables are available
`msg.sender` the address of the caller and `block.timestamp` the current
block timestamp.

@@

\todo{where to add message sender? proposed syntax:}
\begin{lstlisting}
  # ts1 @ f(x) returns z from sdr1 => ts2 @ g(a) returns c from sdr2
\end{lstlisting}

>>>>

Solidity does provide first-order assertion primitives (e.g. @require@ or
@modifier@) but they cannot effectively check function values, which are a
common pattern used in smart contract programs. 
\zz{
On the other hand, assertion primitives are crucial for ensuring the accuracy and 
integrity of a smart contract's business model.
}
\zz{
I'm not sure if this statement applies to the PL community, but from my 
understanding, assertions are typically used during testing rather than runtime. 
However, in smart contracts, these assertions function as guard conditions and can cause reverts if violated, making them extremely important.
}
Programmers have to manually insert such checks around relevant call-sites, \todo{which is bad}.
%Solidity also provides the @modifier@ mechanism that intercepts
%before and after a function call, thus can be used to check
%pre- and post-conditions.
%\todo{can we compose modifier?}
%\todo{can we attach modifier to callbacks?}
%\todo{can we use modifier to check function's argument?}

@@

\todo{restrict possible call targets}
\todo{why static verification fails}
\zz{address vs. function call?}

@@

We develop a core model of the extension, including its syntax,
operational semantics, and discuss its soundness guarantee.
With this extension of higher-order temporal behavioral contracts, we examine
several cases of reported bugs and vulnerabilities and show that
our approach is effective in preventing these attacks. 
\zz{Let's mention the amount of funds we could save if we can prevent these attacks.}
We also evaluate the overhead (gas consumption) of our approach
compared to manually inserted assertion checks, showing that \todo{...}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
	\item We propose a specification of behavioral contracts for expressing and
	      enforcing higher-order and temporal properties for smart contracts.
	\item We design \lang, an extension for Solidity with
	      behavioral contracts, demonstrate its use cases through extensive examples,
	      and how it can improve the safety and reliability.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
	\item We examine a number of real-world attacks and show that our proposal is
	      effective in improving safety and reliability.
	\item We implement our approach on top of the existing Solidity compiler and shows
	      that its runtime overhead is marginal, therefore practical to use.
	\item \zz{Would open-sourcing be considered a contribution? Lol}
\end{itemize}

@@

When specifying the spec of functions, two special variables are available
`msg.sender` the address of the caller and `block.timestamp` the current
block timestamp. 
\zz{How about other special variables, such as `block.chainid` and `tx.origin`?. Perhaps we could redesign a universal syntax for these variables in Section 2.5, where we discuss where to add the message sender}

@@

\todo{where to add message sender? proposed syntax:}
\begin{lstlisting}
  # ts1 @ f(x) returns z from sdr1 => ts2 @ g(a) returns c from sdr2
\end{lstlisting}
\begin{lstlisting}
  # f(x) returns z => g(a) returns c /\ f.msg.sender == g.msg.sender
\end{lstlisting}
